Automated topic naming to support analysis of software maintenance activities

### 2010-08-17 icse/icse2011.tex
Updates to figures. Created new figure directory for clarity and updated latex. Some figures made bigger, added legends.
Signed-off-by: Neil Ernst <neil@neilernst.net>

\begin{figure}
  \centering
 \includegraphics[width=.45\textwidth]{process-model}
 \caption{Research methodology process view.}
  \label{fig:process}
\end{figure}

@@

\begin{table*}
	\centering
\begin{tabular}{c|p{9cm}}
\toprule
\textbf{Label} & \textbf{Related terms} \\
\midrule
\emph{Maintainability} &
testability changeability analyzability stability maintain maintainable modularity modifiability understandability + interdependent dependency encapsulation decentralized modular\\ \hline
\emph{Functionality} &
security compliance accuracy interoperability suitability functional practicality functionality + compliant exploit certificate secured “buffer overflow” policy malicious trustworthy vulnerable vulnerability accurate secure vulnerability correctness accuracy\\ \hline
\emph{Portability} &
conformance adaptability replaceability installability portable movableness movability portability + specification migration standardized l10n localization i18n internationalization documentation interoperability transferability\\ \hline
\emph{Efficiency} &
“resource behaviour” “time behaviour” efficient efficiency + performance profiled optimize sluggish factor penalty slower faster slow fast optimization\\ \hline
\emph{Usability} &
operability understandability learnability useable usable serviceable usefulness utility useableness usableness serviceableness serviceability usability + gui accessibility menu configure convention standard feature focus ui mouse icons ugly dialog guidelines click default human convention friendly user screen interface flexibility\\ \hline
\emph{Reliability} &
“fault tolerance” recoverability maturity reliable dependable responsibleness responsibility reliableness reliability dependableness dependability + resilience integrity stability stable crash bug fails redundancy error failure\\ 
\bottomrule
\end{tabular}
	\caption{NFRs and associated signifiers -- \textsf{exp2}}
	\label{tbl:wnsig}

@@

\todo[inline]{this table should have mysql}
\begin{table}
	\centering
\begin{tabular}{c|c|c|c}
\toprule
Measure & \textsf{exp1} & \textsf{exp2} & \textsf{exp3} \\
\midrule
Named topics   & 281 & 125 & 328  \\
Unnamed topics & 139 & 295 & 92   \\
\bottomrule
\end{tabular}
	\caption{Automatic topic labelling for MaxDB 7.500}
	\label{tbl:wordlist}

@@

\begin{figure*}
  \centering
 \includegraphics[width=.55\textwidth]{unsupervised-bar}
 \caption{ROC values for each NFR, per project and wordlist.}
\todo[inline]{this is too tiny in print}

@@

\begin{figure*}[ht]
\centering
\subfigure[MySQL]{
\includegraphics[width=0.4\textwidth]{mysql-supervised}
\label{fig:subfig1}
}
\subfigure[MaxDB]{
\includegraphics[width=0.4\textwidth]{maxdb-supervised}
\label{fig:subfig2}
}
\label{fig:best-learn-per-tag}
\caption[]{ROC value (black) for the best learner per label, compared with ZeroR accuracy values (grey).
\todo[inline]{better discussion and graphical legend would be nice}
}
\end{figure*}

@@

\begin{figure*}[ht]
\centering
\subfigure[MySQL]{
\includegraphics[width=0.4\textwidth]{multi-label-results-mysql}
\label{fig:subfig3}
}
\subfigure[MaxDB]{
\includegraphics[width=0.4\textwidth]{multi-label-results-maxdb}
\label{fig:subfig4}
}
\label{fig:mulan}
\caption[]{MySQL and MaxDB macro (grey) and micro (black) ROC results per multi-label learner.
\todo[inline]{better discussion and graphical legend would be nice}
}
\end{figure*}

@@

\begin{figure*}
  \centering
  % hi-res version
  %\includegraphics[height=.55\textheight]{maxdb-time-smear-plot-Equal}
  \includegraphics[height=.55\textheight]{small-maxdb-time-smear-plot-Equal}
  % \includegraphics[height=.57\textheight]{small-maxdb-time-smear-plot-Equal}
  \caption{MaxDB 7.500: Labelled topics related to non-functional software qualities plotted over time, continuous topics are trends that occur across time}
  \label{fig:maxdb}
\end{figure*}

\begin{figure*}%[h]
  \centering
  % hi-res version
  %\includegraphics[width=.97\textwidth]{mysql-time-smear-plot-Equal}
  %\includegraphics[width=.97\textwidth]{small-mysql-time-smear-plot-Equal}
  \includegraphics[width=.97\textwidth]{mysql-timeline}
  \caption{MySQL 3.23:NFRs over time. Topic frequency is mapped to alpha (transparency) value.}
  \label{fig:mysql}
\end{figure*}

>>>>

\begin{figure}
  \centering
 \includegraphics[width=.45\textwidth]{figures/process-model}
 \caption{Research methodology process view.}
  \label{fig:process}
\end{figure}

@@

\begin{table*}
	\centering
\begin{tabular}{c|p{9cm}}
\toprule
\textbf{Label} & \textbf{Related terms} \\
\midrule
\emph{Maintainability} &
testability changeability analyzability stability maintain maintainable modularity modifiability understandability interdependent dependency encapsulation decentralized modular\\ \hline
\emph{Functionality} &
security compliance accuracy interoperability suitability functional practicality functionality compliant exploit certificate secured ``buffer overflow'' policy malicious trustworthy vulnerable vulnerability accurate secure vulnerability correctness accuracy\\ \hline
\emph{Portability} &
conformance adaptability replaceability installability portable movableness movability portability specification migration standardized l10n localization i18n internationalization documentation interoperability transferability\\ \hline
\emph{Efficiency} &
``resource behaviour'' ``time behaviour'' efficient efficiency performance profiled optimize sluggish factor penalty slower faster slow fast optimization\\ \hline
\emph{Usability} &
operability understandability learnability useable usable serviceable usefulness utility useableness usableness serviceableness serviceability usability gui accessibility menu configure convention standard feature focus ui mouse icons ugly dialog guidelines click default human convention friendly user screen interface flexibility\\ \hline
\emph{Reliability} &
``fault tolerance'' recoverability maturity reliable dependable responsibleness responsibility reliableness reliability dependableness dependability resilience integrity stability stable crash bug fails redundancy error failure\\ 
\bottomrule
\end{tabular}
	\caption{NFRs and associated signifiers -- \textsf{exp2}}
	\label{tbl:wnsig}

@@

\todo[inline,color=green]{this table should have mysql}
\begin{table}
	\centering
\begin{tabular}{c|c|c|c}
\toprule
Measure & \textsf{exp1} & \textsf{exp2} & \textsf{exp3} \\
\midrule
Named topics   & 281 & 125 & 328  \\
Unnamed topics & 139 & 295 & 92   \\
\bottomrule
\end{tabular}
	\caption{Automatic topic labelling for MaxDB 7.500}
	\label{tbl:wordlist}

@@

\begin{figure*}
  \centering
 \includegraphics[width=.75\textwidth]{figures/unsupervised-bar}
 \caption{ROC values for each NFR, per project and wordlist.}
%\todo[inline]{this is too tiny in print}

@@

\begin{figure*}[ht]
\centering
\subfigure[MySQL]{
\includegraphics[width=0.4\textwidth]{figures/mysql-supervised}
\label{fig:subfig1}
}
\subfigure[MaxDB]{
\includegraphics[width=0.4\textwidth]{figures/maxdb-supervised}
\label{fig:subfig2}
}
\label{fig:best-learn-per-tag}
\caption[]{ROC value (black) for the best learner per label, compared with ZeroR accuracy values (grey).
\todo[inline]{better discussion and graphical legend would be nice}
}
\end{figure*}

@@

\begin{figure*}[ht]
\centering
\subfigure[MySQL]{
\includegraphics[width=0.4\textwidth]{figures/multi-label-results-mysql}
\label{fig:subfig3}
}
\subfigure[MaxDB]{
\includegraphics[width=0.4\textwidth]{figures/multi-label-results-maxdb}
\label{fig:subfig4}
}
\label{fig:mulan}
\caption[]{MySQL and MaxDB macro (grey) and micro (black) ROC results per multi-label learner.
\todo[inline]{better discussion and graphical legend would be nice}
}
\end{figure*}

@@

\begin{figure*}
  \centering
  % hi-res version
  %\includegraphics[height=.55\textheight]{maxdb-time-smear-plot-Equal}
  \includegraphics[height=.55\textheight]{figures/small-maxdb-time-smear-plot-Equal}
  % \includegraphics[height=.57\textheight]{small-maxdb-time-smear-plot-Equal}
  \caption{MaxDB 7.500: Labelled topics related to non-functional software qualities plotted over time, continuous topics are trends that occur across time}
  \label{fig:maxdb}
\end{figure*}

\begin{figure*}%[h]
  \centering
  % hi-res version
  %\includegraphics[width=.97\textwidth]{mysql-time-smear-plot-Equal}
  %\includegraphics[width=.97\textwidth]{small-mysql-time-smear-plot-Equal}
  \includegraphics[width=.97\textwidth]{figures/mysql-timeline}
  \caption{MySQL 3.23:NFRs over time. Topic frequency is mapped to alpha (transparency) value.}
  \label{fig:mysql}
\end{figure*}
